---
title: "Is There different sizes in zooplankton ? "
Catégorie : Data Sciences I 
description: |
  Analysis of different classes of zooplankton to know their size
author:
  - name: Plasman Héloïse
    url: {http://Heloise04.github.io/Heloise_blog/}
date: 11-10-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
SciViews::R
```

```{r importation}
data <- read("zooplankton", package = "data.io")
```

# Introduction and presentation of the data base 

I chose to work mainly with the following data : the size and the class of zooplankton. We will see if the class to which they belong influences or characterizes their size.


```{r graphique}
chart(data = zooplankton, class ~ size %col=% class) +
  ggridges::geom_density_ridges()
```

We can see that Cnidarian and Chaetognath tends to be taller than any other classes of zooplankton. But we can also observe that these 2 classes have a greater distribution in their size and so there are less in each size but they are spread over a larger interval. While most of the other classes appear to be predominantly small.
